---
title: "Diffusion"
author: "Yohan Min"
date: "`r gsub(' 0', ' ', format(Sys.Date(), format='%b %d, %Y'))`"
output:
  html_document:
    keep_md: yes
    preserve_yaml: yes
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE, echo= F}
knitr::opts_chunk$set(echo = FALSE, warning= F, message= F, fig.align="center")
library(tidyverse) # includes all the packages below 
# library(readr)
# library(dplyr)
# library(tidyr)
# library(ggplot2)
# library(tibble)
# library(forcats)
# library(stringr)
library(lubridate)
library(pander)
library(psych)
library (cluster)
library(reshape)
library(reshape2)
library(som)
library(GPArotation)
library(corrplot)
library(GGally)
# library(MASS)
library(faraway)
library(sjPlot)
```


```{r load data}

load("../data/derived/iv.Rdata")
load("../data/derived/dv.Rdata")
load("../data/derived/ts.Rdata")
load("../data/derived/reg.Rdata")
```


# Diffusion of innovation 

> The best policy for residential solar adoption is the local campaign leading to the PV awareness and community active involvement which causes the solar installation spread over the region. 

## PV trend in Seattle
```{r}
load("../data/derived/ts.Rdata")
g_nbor_ts
```

## Impact of NWseed 

```{r}
g_nb_ts
```

* January-April 2011 Queen Anne 30 Queen Anne homes for 130 kilowatts of solar!
* July-October 2011 Magnolia 29 Magnolia homes for 114 kilowatts of solar!
* January-April 2012 NE 52 Northeast Seattle homes for 246 kilowatts of solar!
* January-April 2013 NW 141 Northwest Seattle homes for 640 kilowatts of solar!
* July-October 2013 Central/ SE 185 homes for 885 kilowatts of solar!
* July – October 2014 SW 111 homes for 684 kW

> A function of time and amount - earlier and larger amount of adoption expedites the diffusion!

> The best policy for residential solar adoption is the local campaign leading to the PV awareness and community active involvement which accelerates the solar installation spread over the region. 

```{r}
grid.arrange(p1, p2, p3, nrow = 3)
```

